\documentclass[10pt,a4paper]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{enumitem}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1ex plus 0.5ex minus 0.2ex}

\begin{document}

\begin{center}
    {\huge \textbf{John Doe}} \\[2mm]
    Software Engineer $\vert$ john.doe@email.com $\vert$ (555) 123-4567 $\vert$ github.com/johndoe
\end{center}

\vspace{4mm}
\noindent\textbf{\large Professional Profile} \\
\rule{\linewidth}{0.5pt}

An experienced software engineer with a passion for scalable architectures, microservices, and complex problem solving. Proven track record of delivering high-performance backend systems across distributed cloud environments. Skilled in orchestrating containerized deployments and optimizing critical path execution logic to support millions of concurrent users. Seeking to leverage expertise in distributed systems and performance optimization in a senior leadership role.

\vspace{4mm}
\noindent\textbf{\large Education} \\
\rule{\linewidth}{0.5pt}

\begin{center}
\begin{tabular}{llc}
\toprule
\textbf{Degree} & \textbf{Institution} & \textbf{Year} \\
\midrule
M.S. Computer Science & Stanford University & 2024 \\
B.S. Mathematics & Massachusetts Institute of Technology (MIT) & 2022 \\
\bottomrule
\end{tabular}
\end{center}

\vspace{4mm}
\noindent\textbf{\large Experience} \\
\rule{\linewidth}{0.5pt}

\noindent
\begin{tabularx}{\linewidth}{@{}Xr@{}}
\textbf{Senior Backend Engineer} $\vert$ \textit{TechCorp Inc.} & \textbf{2022 -- Present} \\
\end{tabularx}

\begin{itemize}[leftmargin=*,noitemsep]
    \item Designed and implemented a distributed microservice architecture serving 1M+ daily active users, built entirely on Kubernetes.
    \item Reduced API latency by 40\% through strategic Redis caching and optimizing Postgres queries.
    \item Spearheaded the migration from a monolithic legacy system to event-driven microservices using Apache Kafka.
    \item Mentored junior engineers and led weekly architecture review boards to enforce coding standards.
\end{itemize}

\vspace{2mm}
\noindent
\begin{tabularx}{\linewidth}{@{}Xr@{}}
\textbf{Software Engineer II} $\vert$ \textit{Global Solutions LLC} & \textbf{2020 -- 2022} \\
\end{tabularx}

\begin{itemize}[leftmargin=*,noitemsep]
    \item Developed core features for the enterprise SaaS platform using React and Node.js.
    \item Automated CI/CD pipelines using GitHub Actions, cutting deployment times by 60\%.
    \item Implemented robust unit and integration testing, raising test coverage from 45\% to 92\%.
\end{itemize}

\vspace{2mm}
\noindent
\begin{tabularx}{\linewidth}{@{}Xr@{}}
\textbf{Software Engineering Intern} $\vert$ \textit{Startup Inc.} & \textbf{2019 -- 2020} \\
\end{tabularx}

\begin{itemize}[leftmargin=*,noitemsep]
    \item Built an internal analytics dashboard using Python and Vue.js.
    \item Optimized SQL queries, improving report generation speed by 25\%.
\end{itemize}

\vspace{4mm}
\noindent\textbf{\large Technical Skills} \\
\rule{\linewidth}{0.5pt}

\textbf{Languages:} Python, Go, C++, JavaScript, TypeScript, SQL, Rust \\
\textbf{Frameworks \& Tools:} React, Node.js, Django, FastAPI, Docker, Kubernetes, Apache Kafka, Redis, PostgreSQL, AWS, GCP
\end{document}
